Dynein walks like an Imperial AT-ST

### 2017-11-15 reorganize/papers/paper/paper.tex
Many more filename changes.

\input{../../data/paper_stepping_parameters.tex}

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/paper-plot.pdf}
\caption{Placeholder image of a frog with a long example caption to show justification setting.}
\label{fig:trajectory}
\end{figure}

>>>>

\input{../../data/paper_histogram_stepping_parameters.tex}

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/stepping_length_histogram_paper.pdf}
\caption{Histogram of size of steps taken by model.}
\label{fig:lengthhist}
\end{figure}

\begin{figure}%[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/stepping_time_histogram_paper.pdf}
\caption{Histogram of duration of steps taken by model.}
\label{fig:timehist}
\end{figure}
